<span style="color:red;">Building a house with<br />Advanced Normalization Tools (*ANTs*)</span>

### 2014-09-03 ants2015build.Rmd
WIP: regular update

@@

* Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)

* <span style="color:grey;">
Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)  </span>

* Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)

* <span style="color:grey;"> Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>

* Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)

@@

* Solutions to challenging statistical image processing problems usually need elements from each of the above

>>>>

... in a competitive world ...

@@

* <span style="color:grey;"> Similarity $=$ a function relating one image to another, given a transformation (e.g. mutual information)</span>

* Diffeomorphisms $=$ differentiable map with differentiable inverse (e.g. "silly putty", viscous fluid)

* <span style="color:grey;">Segmentation $=$ labeling tissue or anatomy in images, usually automated (e.g. K-means)</span>

* Multivariate $=$ using many voxels or measurements at once (e.g. PCA, $p >> n$ ridge regression)</span>

* <span style="color:grey;">Multiple modality $=$ using many modalities at once (e.g. DTI and T1 and BOLD)</span>

@@

* <span style="color:grey;">Solutions to challenging statistical image processing problems usually need elements from each of the above</span>
